### 2020-11-30 misc/expo/littlewood-offord.tex
nullstellensatz

Before we get started, let us recall the properties of a {\it normed space}. It is a vector space $B$ over
a field $F$ along with
a function $\norm{\cdot} : B \to \RR$ such that
\medskip
\item{i)} $\norm x\geq 0$ for all $x\in B$;
\smallskip
\item{ii)} $\norm x = 0$ if and only if $x = 0$;
\smallskip
\item{iii)} for every $\lambda \in F$, $\norm{\lambda x} = |\lambda|\norm x$;
\smallskip
\item{iv)} the triangle inequality $\norm{x+y} \leq \norm x + \norm y$ for all $x,y\in B$.
\medskip
Note that in (iii), we have assumed some kind of norm on the field $F$. In the case that $F = \RR$, this
is the ordinary absolute value function, and in the case that $F=\CC$, we can take the modulus.
The {\it distance} between two vectors $x$ and $y$ is the norm of the difference $x-y$.

On a completely different note, we will also need some notions regarding families of subsets of a finite set.
If $X = \{1,2,\ldots,n\}$,
then the power set $2^X$ has a natural partial order given by inclusion. A {\it chain} is a set of subsets
$\{A_1,A_2, \ldots, A_k\}$ of $X$ such that $A_1\subseteq A_2\subseteq\cdots\subseteq A_k$, while an
{\it antichain} or {\it Sperner family} is a family of subsets $\{A_1,A_2\ldots,A_k\}$ such that if $i\neq j$
then $A_i\not\subseteq A_j$, for any $1\leq i,j \leq k$. A chain is {\it maximal} if one cannot add any set
to the family without violating the chain property. A chain can be as large as $|X|+1$, since for example,
we have the maximal chain
$$\emptyset\subseteq \{1\}\subseteq \{1,2\} \subseteq \cdots \subseteq X.$$
How big can an antichain be? Well, we could take every set to be of the same size $i$, and this would certainly
form an antichain. Since ${n\choose i}$ is maximised, when $i =\lfloor n/2\rfloor$, we see that the maximum
size of an antichain must be at least ${n\choose \lfloor n/2\rfloor}$. The following famous theorem shows that
we can do no better.

@@

>>>>

Before we get started, we will also need some notions regarding families of subsets of a finite set.
If $X = \{1,2,\ldots,n\}$,
then the power set $2^X$ has a natural partial order given by inclusion. A {\it chain} is a set of subsets
$\{A_1,A_2, \ldots, A_k\}$ of $X$ such that $A_1\subseteq A_2\subseteq\cdots\subseteq A_k$, while an
{\it antichain} or {\it Sperner family} is a family of subsets $\{A_1,A_2\ldots,A_k\}$ such that if $i\neq j$
then $A_i\not\subseteq A_j$, for any $1\leq i,j \leq k$. A chain is {\it maximal} if one cannot add any set
to the family without violating the chain property. A chain can be as large as $|X|+1$, since for example,
we have the maximal chain
$$\emptyset\subseteq \{1\}\subseteq \{1,2\} \subseteq \cdots \subseteq X.$$
How big can an antichain be? Well, we could take every set to be of the same size $i$, and this would certainly
form an antichain. Since ${n\choose i}$ is maximised, when $i =\lfloor n/2\rfloor$, we see that the maximum
size of an antichain must be at least ${n\choose \lfloor n/2\rfloor}$. The following famous theorem shows that
we can do no better.

@@

P. Erd\H os used Sperner's theorem to give the following neat solution to the Littlewood-Offord problem
in the case $B=\RR$:
